---
output: github_document
---

# `{sarcasm}`

## Usage

```{r setup, include = FALSE}
devtools::load_all()

library(reticulate)

knitr::knit_hooks$set(
    error = function(x, options) {
        paste0( "<pre><code><span style='color: red;'>", sarcastic(x), "<span></pre></code>")
    }
)

knitr::opts_chunk$set(comment = NULL)
```


Produces sArCaStic text from a character vector.

```{r}
set.seed(2)
text = 'pythonistas'
sarcastic(text)
```

```{r}
set.seed(2)
text = c('pythonistas', 'r_users')
sarcastic(text)
```

Comes with shorthand as well.

```{r}
text %>% `/s`
```

## Error handler

Make a mockery of those dreadful errors:

```{r err-handle, error=TRUE, message = FALSE}
sarcastic_errors()
A = rnorm
A[10]
```

Prank your friends by placing this in their `.Rprofile`:

```{r ridicule-err, error = TRUE, message = FALSE, eval = FALSE}
options(ridicule_probability = 1)
demoralizing_errors(silent = TRUE)
A[10]
```

<pre><code><span style='color: red;'>
Error in A[10] : object of type 'closure' is not subsettable. HuZzah Wow WeE YoU'Re a wEll-mAdE cOdEr.
<span></pre></code>



The function makes use of and corrupts the `praise` package to offer mockery
after errors are encountered, optionally with probability specified in the
options to make it an unexpected surprise.


## Installation

```r
remotes::install_github("https://github.com/awong234/sarcasm")
```

# Python module `pysnark`

There is also a python module included:

```{r}
pysnark = reticulate::import_from_path(module = 'pysnark.sarcasm', path = system.file(package = 'sarcasm', 'pysnark'))
pysnark$sarcastic(text)
```

```{r}
pysnark$sarcastic(pysnark$sarcastic)
```

